Linear Ordered Attribute Grammar scheduling using SAT-solving

### 2014-10-09 paper/paper.tex
Fix typo in abstract, add Atze to authors and fix affiliations and title

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tikz}
\input{./formats.tex}

\author{L. Thomas van Binsbergen\inst{1} \and Jeroen Bransen\inst{2} \and Koen Claessen\inst{3}}
\institute{todo, \email{todo@todo.co.uk}
\and Utrecht University, Utrecht, The Netherlands, \email{J.Bransen@uu.nl}
\and todo, \email{koen@chalmers.se}}
\title{SAT-solving Linear Ordered Attribute Grammars}

@@

\begin{abstract}
Attribute grammars are a formalism for describing tree computations (catamorphisms), and are therefore suitable for implementing the semantics of programming languages. A well-known subclass is the class of linear ordered attribute grammars, for which a linear evaluation order can be found statically. The problem of finding such an order is however known to to be NP-hard.

>>>>

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[T1]{fontenc}
\usepackage{tikz}
\input{./formats.tex}

\title{Linear Ordered Attribute Grammar scheduling using SAT-solving}
\author{Jeroen Bransen\inst{1}  \and L. Thomas van Binsbergen\inst{2,1} \and Koen Claessen\inst{3} \and Atze Dijkstra\inst{1}}
\institute{Utrecht University, Utrecht, The Netherlands, \email{\{J.Bransen,atze\}@uu.nl}
\and Royal Holloway, University of London, London, UK, \email{Thomas.VanBinsbergen.2014@live.rhul.ac.uk}
\and Chalmers University of Technology, Gothenburg, Sweden, \email{koen@chalmers.se}}

@@

\begin{abstract}
Attribute grammars are a formalism for describing tree computations (catamorphisms), and are therefore suitable for implementing the semantics of programming languages. A well-known subclass is the class of linear ordered attribute grammars, for which a linear evaluation order can be found statically. The problem of finding such an order is however known to be NP-hard.
